Parallel Solving of Multiple Information-Coordinated Global Optimization Problems

### 2020-05-29 2020/JPDC_MCO/2020_JPDC.tex
Compress references

\begin{equation}\label{eq:2}
D  = \{ y\in R^N: a_i \leq y_i \leq b_i, 1 \leq i \leq N \}
\end{equation}
defined by a set of optimized functions
\begin{equation}\label{eq:3}
F(y) = \{ f_1(y),  f_2(y),\dots, f_s(y) \}
\end{equation}
where $y = (y_1,y_2,\dots,y_N)$ is the vector of varied parameters, $N$ is the dimension of the global optimization problems to be solved, and $D$ is the search domain for the given vectors $a$ and $b$. 
In this paper, it is assumed that the functions $f_i(y)$, $1 \leq i \leq s$, can be multiextremal, and the procedures for calculating the values of these functions at points in the search domain $y \in D$ can be computationally expensive. It is also assumed that the functions $f_i(y)$, $1 \leq i \leq s$, satisfy the Lipschitz condition
\begin{equation}\label{eq:4}
|f_i (y')-f_i (y'')| \leq L_i \|y'-y''\|, y',y''\in D, 1 \leq i \leq s
\end{equation}
where $L_i$ is the Lipschitz constant for the function $f_i(y)$, $1 \leq i \leq s$ and ${\|*\|}$ denotes the Euclidean norm in $R^N$. Fulfillment of the Lipschitz condition allows us to construct numerical estimates of the possible behavior of minimized functions based on a finite set of calculated function values at points in the search domain.

@@

Let $k$, $k \geq 2$ optimization iterations be performed, and the search information $A_k$ from (\ref{eq:13}) is obtained. To adaptively select the points of the next iterations, the optimization algorithm has to evaluate the possibility of placing the global minimum in the subintervals, into which the interval $[0,1]$ is divided by the points $x_i$, $1 \leq i \leq k$, previously performed iterations of the global search. This assessment can be performed by introducing characteristics of the subintervals, the value of which would be proportional to the degree to which the global minimum can be located in these subintervals

@@

\begin{equation}\label{eq:16}
R(i)=(x_i-x_{i-1}), 1 < i \leq k, x_i, x_{i-1} from A_k.
\end{equation}

@@

\begin{equation}\label{eq:17}
R(i)=0.5 H \rho_i - 0.5 (z_{i-1} + z_i), \rho_i=(x_i - x_{i-1})^{1/N}, 1 < i \leq k,
\end{equation}
where $H$ is the H\"older constant from (\ref{eq:12}) for the reduced global optimization problem to be solved; ($N$ is the dimensionality of the problem from (\ref{eq:7})). For the multidimensional generalized global search algorithm (GSA) \cite{c5,c24}, developed in the framework of the information-statistical approach, the characteristic has the form

@@

Again, we note that the above computational scheme is quite general. Within the framework of this scheme, many global search algorithms can be presented, as evidenced, in particular, by the examples given in (\ref{eq:16})-(\ref{eq:18}), as well as other characteristically represented algorithms (see, for example, \cite{c22,c23,c24,c25,c26,c27,c28,c29,c30,c31}). Thus, the parallelization methods discussed in Section \ref{sec:4} can be used for a sufficiently wide variety of global search algorithms.

@@

\bibliography{mybibfile}

>>>>

\begin{equation}\label{eq:2}
D  = \{ y\in R^N: a_i \leq y_i \leq b_i, 1 \leq i \leq N \}
\end{equation}
defined by a set of optimized functions
\begin{equation}\label{eq:3}
F(y) = \{ f_1(y),  f_2(y),\dots, f_s(y) \},
\end{equation}
where $y = (y_1,y_2,\dots,y_N)$ is the vector of varied parameters, $N$ is the dimension of the global optimization problems to be solved, and $D$ is the search domain for the given vectors $a$ and $b$. 
In this paper, it is assumed that the functions $f_i(y)$, $1 \leq i \leq s$, can be multiextremal, and the procedures for calculating the values of these functions at points in the search domain $y \in D$ can be computationally expensive. It is also assumed that the functions $f_i(y)$, $1 \leq i \leq s$, satisfy the Lipschitz condition
\begin{equation}\label{eq:4}
|f_i (y')-f_i (y'')| \leq L_i \|y'-y''\|, y',y''\in D, 1 \leq i \leq s,
\end{equation}
where $L_i$ is the Lipschitz constant for the function $f_i(y)$, $1 \leq i \leq s$, and ${\|*\|}$ denotes the Euclidean norm in $R^N$. Fulfillment of the Lipschitz condition allows us to construct numerical estimates of the possible behavior of minimized functions based on a finite set of calculated function values at points in the search domain.

@@

Let $k$, $k \geq 2$, optimization iterations be performed, and the search information $A_k$ from (\ref{eq:13}) is obtained. To adaptively select the points of the next iterations, the optimization algorithm has to evaluate the possibility of placing the global minimum in the subintervals, into which the interval $[0,1]$ is divided by the points $x_i$, $1 \leq i \leq k$, previously performed iterations of the global search. This assessment can be performed by introducing characteristics of the subintervals, the value of which would be proportional to the degree to which the global minimum can be located in these subintervals

@@

\begin{equation}\label{eq:16}
R(i)=(x_i-x_{i-1}), 1 < i \leq k, \; x_i, x_{i-1} \; \mathrm{from} \; A_k.
\end{equation}

@@

\begin{equation}\label{eq:17}
R(i)=0.5 H \rho_i - 0.5 (z_{i-1} + z_i), \rho_i=(x_i - x_{i-1})^{1/N}, 1 < i \leq k,
\end{equation}
where $H$ is the H\"older constant from (\ref{eq:12}) for the reduced global optimization problem to be solved; $N$ is the dimensionality of the problem from (\ref{eq:7}). For the multidimensional generalized global search algorithm (GSA) \cite{c5,c24}, developed in the framework of the information-statistical approach, the characteristic has the form

@@

Again, we note that the above computational scheme is quite general. Within the framework of this scheme, many global search algorithms can be presented, as evidenced, in particular, by the examples given in (\ref{eq:16})--(\ref{eq:18}), as well as other characteristically represented algorithms (see, for example, \cite{c22,c23,c24,c25,c26,c27,c28,c29,c30,c31}). Thus, the parallelization methods discussed in Section \ref{sec:4} can be used for a sufficiently wide variety of global search algorithms.

@@

\biboptions{sort&compress}
\bibliography{mybibfile}
